Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-09 paper/paper.tex
explaining test cases

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. For all engines engines
we found test using non-portable functions that we detected by running
the test on a different engine. We needed to discard those.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccrc}
    \toprule
    Name & Source & \# JS files & \# JS files final \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 & 29,846\\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 \\
    \veight{} & \cite{v8} & 75 & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 & 921\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878\\
    JSI & \cite{jsi} & 99 & 63 \\
    Tiny-js & \cite{tinyjs} & 49 & 37 \\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesFilter{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Column ``original'' shows the test cases for each
test suite. Overall, we found a total of \totfiles{} JS files. We did
not consider tests from the \chakra{} repository because they depend
on non-portable objects. Notice that the number of tests in
\veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. Column
``compile-in-all'' shows the number of test cases for which all four
engines we analyzed do not throw compile-time error. We discarded
tests that manifest compile errors as they clearly indicate missing
features; these tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, although being part of the spec, not all
engines currently support. Finally, column ``no-fail-in-all'' shows
the tests for which all engines
pass. Section~\ref{sec:transplantation} discusses these failures, some
of which are indicative of bugs. The tests under this column will be
used to create new, potentially fault-revealing, tests. For that, it
is important to assure that all of them pass.

@@

 %% The table shows the
 %%    number of test cases in each test suite considered: TC-39
 %%    conformance test suite, suites from engines we analyzed, and
 %%    suites from other engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & - \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & -\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & -\\
    \veight{} & \cite{v8} & 75 & 57 & -\\
    \midrule    
    Duktape & \cite{duktape} & 1,195 & 921 & -\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & -\\
    JSI & \cite{jsi} & 99 & 63 & -\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & -\\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesFilter{} & -\\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\Mar{remember to say that we use dataset Table II''compile-in-all''.}
